Verifying Demonstrations

### 2020-03-12 paper/DB-Schnorr-nbit.tex
Fixes refs, nbit MF thm
Writes up nbit DH proof

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{2^n}\), where \(m, q\) are as in 
  \cref{DB-Schnorr}.
\end{theorem}

@@

  Thus, the success probability is \(\frac{1}{2}+\frac{1}{2^{|q|-l}}\) per 
  round, or \(\left(\frac{1}{2}+\frac{1}{2^{|q|-l}}\right)^n\) in total.

\end{proof}

>>>>

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then \(
    \Adv_{\DBS}^{\text{MF}}(\adv) =
      \left(\frac{1}{2} + \frac{1}{2^{|q|-l}}\right)^n,
  \) where \(m, q\) are as in \cref{DB-Schnorr-nbit}.
\end{theorem}

@@

  Thus, the success probability is \(\frac{1}{2}+\frac{1}{2^{|q|-l}}\) per 
  round, or \(\left(\frac{1}{2}+\frac{1}{2^{|q|-l}}\right)^n\) in total.
\end{proof}

\paragraph{\Acl{DBDH}}

The protocol is also secure against distance hijacking due to the fact that the 
authenticating bit string is used during the \ac{DB} phase.
(Brands-Chaum used the challenge bit string, something that made their protocol 
vulnerable.)
\Ac{DBDH} requires that the adversary finds a collision between his response 
and that of the honest prover.
Thus the probability of success is equivalent to a collision for the responses 
for the chosen challenge --- in each round.

\begin{theorem}[\acs*{DBDH}/\acs*{DBDF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{2^n}\).
\end{theorem}

\begin{proof}
  The honest prover will choose \(\rho\) such that \(R = g^\rho\).
  The adversary can send his own \(R' = g^{\rho'}\) to the verifier, or let 
  \(R' = R\) to not interfere.

  The verifier will choose \(c_0, \dotsc, c_1\).
  The honest prover will compute \(s_i = \rho - c_i \alpha\), where \(\alpha\) 
  is his secret.
  If the adversary chose \(R' = g^{\rho'}\), he can compute \(s_i' = \rho' - 
  c_i \alpha'\), where \(\alpha'\) is the adversary's secret.
  If the adversary didn't choose \(R'\), he can only guess the values for 
  \(s_i'\).

  During the fast phase, the adversary has two options:
  for each challenge bit, the adversary can \(\Commit\) to a response bit or to 
  \(\Prompt\) the honest prover to send a bit.

  If the adversary chose \(R'\), then he knows \(\rho'\) and can compute the 
  correct \(s_i' = \rho' - c_i \alpha'\) for \(i\in \bin\).
  If the adversary \(\Commit\)s:
  Now, the adversary must commit to one bit of \(s_0'\) or \(s_1'\) before 
  seeing the verifier's choice \(b_i\).
  He can make a guess~\(\hat b\) at the verifier's choice~\(b\).
  Then he commits to the next bit of \(s_{\hat b}'\).
  If the challenge~\(b_i \neq \hat b\), he will commit to the same bit for the 
  next round.
  If indeed \(\hat b = b\), the verifier will accept.
  The success probability is \(\frac{1}{2}\) over all bits.

  If the adversary \(\Prompt\)s:
  The prover computed \(s_0\) and \(s_1\) using \(\rho\) and \(\alpha\).
  However, the verifier will use \(R'\) and \(A'\) in the verification step.
  This will succeed if \(s_b = s_b'\), the probability of which is 
  \(\frac{1}{q}\).
  This means that the probability of success for prompting a bit is 
  \(\frac{1}{2}\), or \(\frac{1}{2^{|q|}}\) over all bits.

  If the adversary didn't choose \(R'\) he consequently doesn't know \(\rho\) 
  and cannot compute the correct \(s_0\) and \(s_1\).
  Thus, committing yields \(\frac{1}{2}\) probability per bit.
  The same applies for prompting.

  Obviously, the better strategy for the adversary is to choose \(R' = 
  g^{\rho'}\).
  It's also a better strategy to \(\Commit\) (\ac{DBDF}) rather than 
  \(\Prompt\) (\ac{DBDH}).
  We thus have that
  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \frac{1}{2^n}\) for \(n\) rounds,
  which concludes the proof.
\end{proof}
